Multi-stream portrait of the Cosmic web

### 2018-03-07 Draft/Chapter3/Source_v2/draft.tex
initial commit

\begin{comment}
\documentclass[useAMS, usenatbib]{mn2e}

@@

\begin{keywords}
methods: numerical -- cosmology: theory -- dark matter -- large-scale structure of Universe 
\end{keywords}
\end{comment}

\chapter{Multi-stream portrait of the Cosmic web}

@@

The problem of objective identification and quantitative characterization of anisotropic structures 
in the distribution of galaxies in space emerged after the first evidences of their existence
(see the review by \citealt{Oort1983} and the references therein). The first theoretical model predicting highly anisotropic concentrations in the mass distribution coming into existence at the non-linear stage of gravitational instability is known as the Zeldovich Approximation (the ZA) (\citealt{Zeldovich1970}, for further developments see also \citealt{Shandarin1989} and the references therein). The ZA predicted the formation of  `pancakes'  also known as the walls in the currently popular jargon. The later development
of the model by \citet{Arnold1982} predicted the formation of filaments along with the pancakes. \citet{Klypin1983a} and \citet{Shandarin1984} demonstrated that the filaments emerge in the cosmological N-body simulation in three-dimensional space.
However, they failed to identify the pancakes at $z=0$. Both the existence of filaments connecting compact clumps of matter and absence of pancakes were confirmed by \citet{Frenk1983}. Puzzled by the absence of the pancakes \citet{Klypin1983a}
speculated that insufficient mass resolution of the simulation was the cause  of the negative outcome. 
This has been unambiguously confirmed by recent simulations using a better numerical technique of computing a density field from the particle
coordinates in cosmological N-body simulations (~\citealt{Shandarin2012} and ~\citealt{Abel2012}). \citealt{Klypin1983a} 
also stressed that the most of filaments are  incorporated in 
`a single three-dimensional web structure'\footnote{The term `cosmic web' was coined by  \citet{Bond1996}.}. 
They admitted that
their simulation did not allow them to confirm the existence of pancakes between the filaments predicted by the ZA \citep{Arnold1982}.

Although the four archetypical elements of the cosmic web:  voids, walls/pancakes, filaments and haloes 
were predicted by ZA and confirmed in cosmological N-body simulation their identification and quantitative characterization
remains under vigorous debate
(see e.g. \citealt{Colberg2008}, \citealt{Elahi2013}, \citealt{Knebe2013}, \citealt{Hoffmann2014}).
The dark matter haloes are arguably the easiest objects to identify in N-body simulations. They can also be reliably associated with
observed objects like galaxies and clusters of galaxies.  But even in this case \citet{Knebe2013} refer to almost thirty different
halo finders suggested after 2000. Identifying filaments and pancakes/walls is far more controversial in both N-body simulations 
and galaxy catalogues. For instance, even estimating the global parameters of the  web  in N-body simulation such as the fractions of volume and mass
in voids, walls/pancakes, filaments and haloes produced quite different results. The estimates of volume 
fractions of voids range from 13  to 86\%  (\citealt{Cautun2014a}, \citealt{Falck2015}, \citealt{Forero-Romero2009a} , \citealt{Hahn2007} , \citealt{Aragon-Calvo2010a}). Similar estimates for walls/pancakes, filaments 
and haloes  are respectively 5-56\% 2-26\% and 0.1-1\%.  Estimates of the mass content vary in large ranges as well.

Large differences in the estimates of volume and mass fractions made by different groups are not surprising if we recognize
considerable differences in the definitions of the components of the cosmic web and numerical methods used in the estimates. Without trying to provide an exhaustive review of all definitions and techniques used for the quantitative morphological 
analysis of the web  we just briefly describe a few approaches in order to illustrate how different they could be. 
Some groups study the web morphology using only coordinates of simulation particles, while others use the particle velocities too. 
Transforming data from  point sets to the density and other fields on a grid is also often used
because fields allow to use a variety of mathematical techniques not available for the particle sets.
However this step can be done by a variety of methods some as simple as cloud-in-cell (CIC), or more complicated as smoothed-particle hydrodynamics (SPH), 
or using Voronoi and Delaunay tessellations
as in the Delaunay Tessellation Field Estimator (DTFE) method (~\citealt{Weygaert2009}, \citealt{Cautun2014a}).  
Recently a new method called a discrete persistent structure extractor (DisPerSE \citealt{Sousbie2011a},  \citealt{Sousbie2011b} allowing to identify haloes and other components of the web directly from the particles 
has been designed.  This method can be applied to the galaxy catalogues, for instance \citet{Sousbie2011b} applied it to SDSS catalogue and extracted the filaments (which are made available online).

@@

The regions with multi-stream flow constitute the web while the regions with only one stream form
voids (\citealt{Shandarin2011}, ~\citealt{Shandarin2012}, ~\citealt{Abel2012},~\citealt{Falck2012}).
This definition of voids states that in a given N-body simulation, no haloes can be formed before the first
shell crossings have occurred and the smallest haloes cannot be smaller than the mass corresponding 
to the small scale cut-off in the initial power spectrum regardless of the cause of the cut-off:  physical or due to numerical
limitations (see e.g. \citealt{Angulo2013}).  This definition of voids is physical by nature and thus has no  free parameters. In addition, it does not speculate on the sub-grid physical processes.
The first three-stream flow regions are similar to the pancakes in the ZA.
They quickly grow and merge into a complicated three-dimensional structure; filaments making the framework of the web manifest 
themselves at the pancake crossings,  and haloes emerge at the filament crossings. At later times  different parts of the web participating
in the large-scale motion overlap  which increases the web complexity further.

Using the full six-dimensional information allows one to generate new fields which  provide 
additional useful information about the evolution and morphology of the  web. 
One of them is a multi-stream field in Eulerian space, which will be the focus of this paper. 
Another example is the flip-flop field in Lagrangian space. In cosmological context it was first used in the ZA.
\citet{Vogelsberger2011} used it in a study of multi-stream structure of galaxy size haloes.
\citet{Shandarin2014} applied it for identifying subhaloes  in dark matter haloes.
A similar although somewhat simplistic realization of this idea has been revealed in the ORIGAMI method
used for the analysis of the web ( \citealt{Falck2012},  \citealt{Falck2015} ).
 Although these fields cannot be used directly on observational data because the full phase-space information
 is not available, they provide much deeper insight into non-linear clustering of collision-less dark matter
and reveal new features of the web.

@@

In order to compute the multi-stream field we will use the tessellation scheme described in
 \citet{Shandarin2012} which is  also briefly discussed in Section \ref{subsec:method}.
  Using this methodology on the entire simulation box, we discuss the global behaviour of the number of streams in the cosmic web in Section \ref{sec:global}. 
  The tessellation technique we have utilized can be used to find multi-stream fields in smaller Eulerian boxes with very high resolution too. In Section \ref{sec:local} we study the local behaviour of multi-streams flows in regions around haloes the detected using friends-of-friends (FOF) technique.

@@

We have utilized the data from cosmological N-body simulations by Gadget-2 \citep{Springel2005} for 100 $h^{-1}$ Mpc  and 200 $h^{-1}$ Mpc box 
sizes with $128^3$, $256^3$ and $512^3$ grids. Each particle is between  $10^9 - 10^{12} M_{\odot}$. 
The initial conditions and cosmological parameters are consistent with the Planck cosmology. We utilize the initial Lagrangian box and do a three-dimensional mapping onto corresponding evolved simulations. In addition, for local multi-stream analyses around haloes, we have utilized halo catalogues for each of these simulation boxes. These haloes are detected using FOF method considering objects with more than 20 particles found at linking length, $ b= 0.2$.  
%-------------------------------------------------------------------------------------------------------------------------------
\section{Multi-stream field calculation}
\label{subsec:method}

Phase space tessellation considers the dynamics of the particles similar to that of a standard N-body code. 
However the particles are nodes of the tessellation, and are just massless tracers of the flow.
Assuming that the uniform state is modelled by a simple rectangular grid, the particles are the nodes of the grid.
Each elementary cube of the grid is tessellated by five tetrahedra (\citealt{Shandarin2012}\footnote{For the description of an alternative type of the tessellation see \citet{Abel2012}.}) of which the vertices are the
vertices of the cube. Mass is assumed to be uniformly distributed within each tetrahedron and the tessellation remain
intact at all times. The tetrahedra of the tessellation change their shapes and volumes, the latter are used for
computing the densities of the tetrahedra. Despite the complicated deformations experienced by the three-dimensional
sub-manifold tessellated by the tetrahedra, it remains continuous. Projected on three-dimensional configuration space, the tetrahedra
may form complicated structures. The number of streams at a chosen point {\bf x} is simply the number of tetrahedra that contain the point. The diagnostic points are computationally convenient to choose on a regular grid which can be significantly finer than the original grid in Lagrangian space. The ratio of separation of particles on the initial unperturbed grid to the separation distance of points in the diagnostic grid  $l_{\rm part}/l_{\rm dg} $ will be referred to as the refinement factor in the rest of the paper.

Number of streams are odd-valued in the entire configuration space, except in a set of points of measure zero where caustics are formed.  
 A single-stream flow implies that the tetrahedra do not overlap in the corresponding region and thus defined as a void region.
 The web is defined as a set of non-void regions, i.e. the set of regions where the number of stream is equal to or more than three.
 The level of non-linearity in the web  can be quantitatively characterized by using `number of streams' as a parameter. As shown in  \citep{Shandarin2012} there is no simple local relation between the number of streams and density, however the both
 fields are obviously correlated.

@@

The 3-dimensional multi-stream field for the entire simulation box exhibits cosmic web structure with void, walls, filaments and haloes. We propose the number of streams, `$n_{str}$' as a parameter for characterizing and distinguishing structures in the universe. This is different from \citet{Falck2015}, 
where the authors have identified voids, walls, filaments and haloes by particles which have undergone any number of flip-flops along 0, 1, 2 or 3 axes respectively. 
Their description of voids is close to ours except that some particles that have  experienced no flip-flops might be in the region
of multi stream flow formed by other particles.
Thus we expect that the mass fraction in voids defined as the regions with $n_{str} = 1$ is somewhat lower than that defined as the particles with 
flip-flops $= 0$ only at the final state. This is because some particles may have already fallen in the web but  have not experienced flip flop yet and 
some particles that have experienced an even number of flip flops may come back to the original order. However the above arguments are valid only if the thickness of the web is the same in the both approaches. As we discuss below the thickness of the web in our analysis is about (100\% - 84\%)/(100\%-93\%)=2.3 times thinner than in  the analysis by \citet{Falck2015} (See Table \ref{tab:Compare} for details). However  \citet{Falck2015} discussed these effects and claimed that they were small.
%This description is entirely physically motivated, hence the unambiguous definition.

@@

\begin{figure}
 \centering\includegraphics[width=18.5cm]{Chapter3/Source_v2/fig1.pdf} 
\caption{The cosmic web structure in a slice of  $30 h^{-1} \text{Mpc} \times 100 h^{-1} \text{Mpc} \times 100 h^{-1} \text{Mpc}$ in a simulation box of size $100 h^{-1}$ Mpc and $128^3$ particles. Regions with 17 or more streams (blue) form a filamentary structure. The haloes determined by FOF (red) are predominantly embedded in the intersections of the filaments.}
\label{fig:full}
\end{figure}

@@

The single-stream flow, which corresponds to the void, occupies majority of volume of the simulation box (Fig. \ref{fig:m_v_fr}). As mentioned in Section \ref{sec:global}, higher multi-streaming flow regions are nested inside the lower streaming regions. Thus the volume occupied by higher number of streams monotonically decreases with the number of streams. This relation is approximately found to be a power law. For the box of size $L =100 ~h^{-1}$ Mpc and $N = 128^3$ particles ($L/N = 0.78 ~h^{-1}$ Mpc), the volume fraction corresponding to each value of number of streams, $ f_{vol}(n_{str})$ in the multi-stream field calculated with refinement factor of 8 (i.e. the multi-stream field
was computed on 1024$^3$ grid as described in \cite{Shandarin2012}) is 
\begin{equation}
\label{eq:fr_vol}
f_{vol}(n_{str}) =  0.69 n_{str}^{-2.5}
\end{equation}

@@

\begin{figure}
\begin{minipage}[t]{.99\linewidth}
  \centering\includegraphics[width=10.cm]{Chapter3/Source_v2/fig2} 
\end{minipage}\hfill
\caption{Volume and mass fraction of each stream, mean density of each stream in a box of size 100 $h^{-1}$ Mpc and  $128^3$ particles. Exact values of fractions, density and their curve fit for the range $n_{str} \ge 5 $ from Eq.~\ref{eq:fr_vol}, Eq.~\ref{eq:fr_mass} and Eq.~\ref{eq:den} are shown. Multi-streams are calculated with refinement factor of 8. The void ($n_{str} = 1$) occupies 93$\%$ of the volume and 55$\%$ of the mass. }
\label{fig:m_v_fr}
\end{figure}

@@

One of the advantages of using tessellation is the freedom to compute densities at very high resolutions (\cite{Abel2012}, \cite{Shandarin2012}). We remind that the parameter `refinement factor' denotes the ratio of separation of the particles to the separation distance of points in the diagnostic grid as defined in Sec. 3. High refinement factors are extensively used in understanding stream behaviour not only in the halo environment, but inside the halo too (Section ~\ref{sec:local}). The volume fractions of resulting number of streams are
%normalized by multi-stream field resolution (i.e. dividing by the cube of refinement factor) are %
similar for all refinement factors as
shown in bottom of the Fig. ~\ref{fig:Vfr_all} and in Table ~\ref{tab:Compare_ref}. % Hence our triangulation algorithm is universal in the sense that it is independent of the refinement factors used in tessellating the box.   
Multi-stream fields calculated on low refinement factors are more noisy at high number of streams.

With same refinement factors, the mass fractions exhibit similar pattern for same $L/N$ as well (Fig.~\ref{fig:Mfr_all}). The simulation box with highest inter-particle distance (thus least mass resolution) has more mass particles in single streaming region, as tabulated in Table~\ref{tab:Compare_LN}, but decreases steeply thereafter (Table ~\ref{tab:Compare_Slopes}). Unlike the volume fraction, the behaviour of mass fraction has a systematic variation across different refinement factors. The mass fractions given in Table ~\ref{tab:Compare_ref} show that the single-streaming regions in the multi-stream fields with refinement factors 1 and 2 have higher mass fraction than in the fields with refinement factor of 8. Decreasing the resolution from refinement factor of 8 to 1 effectively introduces smoothing of the structure. This results in growth of mass fraction in voids ($n_{str} = 1$) and decreasing it in the web ($n_{str} > 1$). The multi-stream field is more robust as one can see in Fig.~\ref{fig:Vfr_all}. and \ref{fig:Mfr_all}. In addition, the less refined multi-stream grids are prone to noise at high $n_{str}$ as usual.
\begin{figure}
\begin{minipage}[t]{.99\linewidth}
 \centering\includegraphics[width=10.cm]{Chapter3/Source_v2/fig3a} 
  \centering\includegraphics[width=10.cm]{Chapter3/Source_v2/fig3b}
\end{minipage}\hfill
\caption{Top: Volume fraction distribution of streams in 6 simulation boxes of size 100 $h^{-1}$ Mpc, 200 $h^{-1}$ Mpc 
and $128^{3}$, $256^{3}$, $512^{3}$ grids (with refinement factor of 1). Volume fractions are similar for simulation boxes with same inter-particle resolution. Slopes of the curve fits are shown in Table ~\ref{tab:Compare_Slopes}. Bottom: Volume fraction distribution for different refinement factors for 100 $h^{-1}$ Mpc, $128^{3}$ box. A considerably smoother volume fraction distribution is obtained at high number of streams in multi-stream fields with high refinement factor. }
\label{fig:Vfr_all}
\end{figure}

@@

  \centering\includegraphics[width=10.cm]{Chapter3/Source_v2/fig4a} 
  \centering\includegraphics[width=10.cm]{Chapter3/Source_v2/fig4b}
\end{minipage}\hfill
\caption{Top: Mass fraction distribution of streams in 6 simulation boxes of size 100 $h^{-1}$ Mpc, 200 $h^{-1}$ Mpc 
and $128^{3}$, $256^{3}$, $512^{3}$ grids ( with refinement factor of 1). Mass fractions are similar for simulation boxes with same inter-particle resolution. Slopes of the curve fits are shown in Table ~\ref{tab:Compare_Slopes}. Bottom: Mass fraction distribution for different refinement factors for 100 $h^{-1}$ Mpc, $128^{3}$ box. Single-streaming void regions have more fraction of mass particles in multi-stream fields calculated at low refinement factors of 1 and 2. This effect is minimized when calculation is done at better refinement. In addition, mass fraction distribution is less noisy.}
\label{fig:Mfr_all}
\end{figure}

\begin{table}
  \caption{Comparison of the approximate power law dependences of curve fits in Fig. \ref{fig:Vfr_all} and Fig. \ref{fig:Mfr_all}. Power law relations for volume fraction $f_{vol}(n_{str})$ and mass fractions $f_{mass} (n_{str}) $ as a function of number of streams at $n_{str} \geq 5$ are shown (amplitudes are not shown). The boxes of size 100 $h^{-1}$ Mpc on  $128^{3}$ grids and, 200 $h^{-1}$ Mpc on  $256^{3}$ grids have same  $L/N = 0.78 h^{-1}$ Mpc. Similarly, $L/N = 0.39 h^{-1}$ Mpc for boxes of size 100 $h^{-1}$ Mpc on  $256^{3}$ grids and, 200 $h^{-1}$ Mpc on  $512^{3}$ grids.}
\begin{tabular}{|l|r|r|r|r|}
\hline
%\multicolumn{1}{|c|}{} & \multicolumn{4}{l|}{Multi-stream analysis (This work)} & \multicolumn{4}{c|}{ORIGAMI \citep{Falck_Neyrinck:14}}    \\ \hline
$L/N$                & $0.19$ & $0.39$& $0.78$ & $1.56$  \\ \hline
$f_{vol} (n_{str}) $ Vs. $n_{str}$                 & $-2.1$   & $-2.3$    & $-2.5$      & $-2.9$  \\ \hline
$f_{mass} (n_{str}) $   Vs. $n_{str}$            & $-1.1$   & $-1.2$   & $-1.4$       & $-2.0$     \\ \hline
\end{tabular}
 \label{tab:Compare_Slopes}
\end{table}

>>>>

\documentclass[useAMS, usenatbib]{mn2e}

@@

\begin{keywords}
methods: numerical -- cosmology: theory -- dark matter -- large-scale structure of Universe 
\end{keywords}

@@

The problem of objective identification and quantitative characterization of anisotropic structures 
in the distribution of galaxies in space emerged after the first evidences of their existence
(see the review by \citealt{Oort:83} and the references therein). The first theoretical model predicting highly anisotropic concentrations in the mass distribution coming into existence at the non-linear stage of gravitational instability is known as the Zeldovich Approximation (the ZA) (\citealt{Zeldovich_aap:70}, for further developments see also \citealt{Shandarin_Zeldovich:89} and the references therein). The ZA predicted the formation of  `pancakes'  also known as the walls in the currently popular jargon. The later development
of the model by \citet{Arnold_etal:82} predicted the formation of filaments along with the pancakes. \citet{Klypin_Shandarin:83} and \citet{Shandarin_Klypin:84} demonstrated that the filaments emerge in the cosmological N-body simulation in three-dimensional space.
However, they failed to identify the pancakes at $z=0$. Both the existence of filaments connecting compact clumps of matter and absence of pancakes were confirmed by \citet{Frenk_etal:83}. Puzzled by the absence of the pancakes \citet{Klypin_Shandarin:83}
speculated that insufficient mass resolution of the simulation was the cause  of the negative outcome. 
This has been unambiguously confirmed by recent simulations using a better numerical technique of computing a density field from the particle
coordinates in cosmological N-body simulations (~\citealt{Shandarin_etal:12} and ~\citealt{Abel_etal:12}). \citealt{Klypin_Shandarin:83} 
also stressed that the most of filaments are  incorporated in 
`a single three-dimensional web structure'\footnote{The term `cosmic web' was coined by  \citet{Bond_etal:96}.}. 
They admitted that
their simulation did not allow them to confirm the existence of pancakes between the filaments predicted by the ZA \citep{Arnold_etal:82}.

Although the four archetypical elements of the cosmic web:  voids, walls/pancakes, filaments and haloes 
were predicted by ZA and confirmed in cosmological N-body simulation their identification and quantitative characterization
remains under vigorous debate
(see e.g. \citealt{Colberg_etal:08}, \citealt{Elahi_etal:13}, \citealt{Knebe_etal:13}, \citealt{Hoffmann_etal:14}).
The dark matter haloes are arguably the easiest objects to identify in N-body simulations. They can also be reliably associated with
observed objects like galaxies and clusters of galaxies.  But even in this case \citet{Knebe_etal:13} refer to almost thirty different
halo finders suggested after 2000. Identifying filaments and pancakes/walls is far more controversial in both N-body simulations 
and galaxy catalogues. For instance, even estimating the global parameters of the  web  in N-body simulation such as the fractions of volume and mass
in voids, walls/pancakes, filaments and haloes produced quite different results. The estimates of volume 
fractions of voids range from 13  to 86\%  (\citealt{Cautun_etal:14}, \citealt{Flack_Neyrinck:14}, \citealt{Forero_etal:09} , \citealt{Hahn_etal:07} , \citealt{Aragon_etal:10}). Similar estimates for walls/pancakes, filaments 
and haloes  are respectively 5-56\% 2-26\% and 0.1-1\%.  Estimates of the mass content vary in large ranges as well.

Large differences in the estimates of volume and mass fractions made by different groups are not surprising if we recognize
considerable differences in the definitions of the components of the cosmic web and numerical methods used in the estimates. Without trying to provide an exhaustive review of all definitions and techniques used for the quantitative morphological 
analysis of the web  we just briefly describe a few approaches in order to illustrate how different they could be. 
Some groups study the web morphology using only coordinates of simulation particles, while others use the particle velocities too. 
Transforming data from  point sets to the density and other fields on a grid is also often used
because fields allow to use a variety of mathematical techniques not available for the particle sets.
However this step can be done by a variety of methods some as simple as cloud-in-cell (CIC), or more complicated as smoothed-particle hydrodynamics (SPH), 
or using Voronoi and Delaunay tessellations
as in the Delaunay Tessellation Field Estimator (DTFE) method (~\citealt{Weygaert_Schaap:09}, \citealt{Cautun_etal:14}).  
Recently a new method called a discrete persistent structure extractor (DisPerSE \citealt{Sousbie:11},  \citealt{Sousbie_etal:11} allowing to identify haloes and other components of the web directly from the particles 
has been designed.  This method can be applied to the galaxy catalogues, for instance \citet{Sousbie_etal:11} applied it to SDSS catalogue and extracted the filaments (which are made available online).

@@

The regions with multi-stream flow constitute the web while the regions with only one stream form
voids (\citealt{Shandarin:11}, ~\citealt{Shandarin_etal:12}, ~\citealt{Abel_etal:12},~\citealt{Flack_etal:12}).
This definition of voids states that in a given N-body simulation, no haloes can be formed before the first
shell crossings have occurred and the smallest haloes cannot be smaller than the mass corresponding 
to the small scale cut-off in the initial power spectrum regardless of the cause of the cut-off:  physical or due to numerical
limitations (see e.g. \citealt{Angulo_etal:13}).  This definition of voids is physical by nature and thus has no  free parameters. In addition, it does not speculate on the sub-grid physical processes.
The first three-stream flow regions are similar to the pancakes in the ZA.
They quickly grow and merge into a complicated three-dimensional structure; filaments making the framework of the web manifest 
themselves at the pancake crossings,  and haloes emerge at the filament crossings. At later times  different parts of the web participating
in the large-scale motion overlap  which increases the web complexity further.

Using the full six-dimensional information allows one to generate new fields which  provide 
additional useful information about the evolution and morphology of the  web. 
One of them is a multi-stream field in Eulerian space, which will be the focus of this paper. 
Another example is the flip-flop field in Lagrangian space. In cosmological context it was first used in the ZA.
\citet{Vogelsberger_etal:11} used it in a study of multi-stream structure of galaxy size haloes.
\citet{Shandarin_Medvedev:14} applied it for identifying subhaloes  in dark matter haloes.
A similar although somewhat simplistic realization of this idea has been revealed in the ORIGAMI method
used for the analysis of the web ( \citealt{Flack_etal:12},  \citealt{Flack_Neyrinck:14} ).
 Although these fields cannot be used directly on observational data because the full phase-space information
 is not available, they provide much deeper insight into non-linear clustering of collision-less dark matter
and reveal new features of the web.

@@

In order to compute the multi-stream field we will use the tessellation scheme described in
 \citet{Shandarin_etal:12} which is  also briefly discussed in Section \ref{subsec:method}.
  Using this methodology on the entire simulation box, we discuss the global behaviour of the number of streams in the cosmic web in Section \ref{sec:global}. 
  The tessellation technique we have utilized can be used to find multi-stream fields in smaller Eulerian boxes with very high resolution too. In Section \ref{sec:local} we study the local behaviour of multi-streams flows in regions around haloes the detected using friends-of-friends (FOF) technique.

@@

We have utilized the data from cosmological N-body simulations by Gadget-2 \citep{Springel:05} for 100 $h^{-1}$ Mpc  and 200 $h^{-1}$ Mpc box 
sizes with $128^3$, $256^3$ and $512^3$ grids. Each particle is between  $10^9 - 10^{12} M_{\odot}$. 
The initial conditions and cosmological parameters are consistent with the Planck cosmology. We utilize the initial Lagrangian box and do a three-dimensional mapping onto corresponding evolved simulations. In addition, for local multi-stream analyses around haloes, we have utilized halo catalogues for each of these simulation boxes. These haloes are detected using FOF method considering objects with more than 20 particles found at linking length, $ b= 0.2$.  
%-------------------------------------------------------------------------------------------------------------------------------
\section{Multi-stream field calculation}
\label{subsec:method}

Phase space tessellation considers the dynamics of the particles similar to that of a standard N-body code. 
However the particles are nodes of the tessellation, and are just massless tracers of the flow.
Assuming that the uniform state is modelled by a simple rectangular grid, the particles are the nodes of the grid.
Each elementary cube of the grid is tessellated by five tetrahedra (\citealt{Shandarin_etal:12}\footnote{For the description of an alternative type of the tessellation see \citet{Abel_etal:12}.}) of which the vertices are the
vertices of the cube. Mass is assumed to be uniformly distributed within each tetrahedron and the tessellation remain
intact at all times. The tetrahedra of the tessellation change their shapes and volumes, the latter are used for
computing the densities of the tetrahedra. Despite the complicated deformations experienced by the three-dimensional
sub-manifold tessellated by the tetrahedra, it remains continuous. Projected on three-dimensional configuration space, the tetrahedra
may form complicated structures. The number of streams at a chosen point {\bf x} is simply the number of tetrahedra that contain the point. The diagnostic points are computationally convenient to choose on a regular grid which can be significantly finer than the original grid in Lagrangian space. The ratio of separation of particles on the initial unperturbed grid to the separation distance of points in the diagnostic grid  $l_{\rm part}/l_{\rm dg} $ will be referred to as the refinement factor in the rest of the paper.

Number of streams are odd-valued in the entire configuration space, except in a set of points of measure zero where caustics are formed.  
 A single-stream flow implies that the tetrahedra do not overlap in the corresponding region and thus defined as a void region.
 The web is defined as a set of non-void regions, i.e. the set of regions where the number of stream is equal to or more than three.
 The level of non-linearity in the web  can be quantitatively characterized by using `number of streams' as a parameter. As shown in  \citep{Shandarin_etal:12} there is no simple local relation between the number of streams and density, however the both
 fields are obviously correlated.

@@

The 3-dimensional multi-stream field for the entire simulation box exhibits cosmic web structure with void, walls, filaments and haloes. We propose the number of streams, `$n_{str}$' as a parameter for characterizing and distinguishing structures in the universe. This is different from \citet{Flack_Neyrinck:14}, 
where the authors have identified voids, walls, filaments and haloes by particles which have undergone any number of flip-flops along 0, 1, 2 or 3 axes respectively. 
Their description of voids is close to ours except that some particles that have  experienced no flip-flops might be in the region
of multi stream flow formed by other particles.
Thus we expect that the mass fraction in voids defined as the regions with $n_{str} = 1$ is somewhat lower than that defined as the particles with 
flip-flops $= 0$ only at the final state. This is because some particles may have already fallen in the web but  have not experienced flip flop yet and 
some particles that have experienced an even number of flip flops may come back to the original order. However the above arguments are valid only if the thickness of the web is the same in the both approaches. As we discuss below the thickness of the web in our analysis is about (100\% - 84\%)/(100\%-93\%)=2.3 times thinner than in  the analysis by \citet{Flack_Neyrinck:14} (See Table \ref{tab:Compare} for details). However  \citet{Flack_Neyrinck:14} discussed these effects and claimed that they were small.
%This description is entirely physically motivated, hence the unambiguous definition.

@@

\begin{figure}
 \centering\includegraphics[width=8.5cm]{fig1} 
\caption{The cosmic web structure in a slice of  $30 h^{-1} \text{Mpc} \times 100 h^{-1} \text{Mpc} \times 100 h^{-1} \text{Mpc}$ in a simulation box of size $100 h^{-1}$ Mpc and $128^3$ particles. Regions with 17 or more streams (blue) form a filamentary structure. The haloes determined by FOF (red) are predominantly embedded in the intersections of the filaments.}
\label{fig:full}
\end{figure}

@@

The single-stream flow, which corresponds to the void, occupies majority of volume of the simulation box (Fig. \ref{fig:m_v_fr}). As mentioned in Section \ref{sec:global}, higher multi-streaming flow regions are nested inside the lower streaming regions. Thus the volume occupied by higher number of streams monotonically decreases with the number of streams. This relation is approximately found to be a power law. For the box of size $L =100 ~h^{-1}$ Mpc and $N = 128^3$ particles ($L/N = 0.78 ~h^{-1}$ Mpc), the volume fraction corresponding to each value of number of streams, $ f_{vol}(n_{str})$ in the multi-stream field calculated with refinement factor of 8 (i.e. the multi-stream field
was computed on 1024$^3$ grid as described in \cite{Shandarin_etal:12}) is 
\begin{equation}
\label{eq:fr_vol}
f_{vol}(n_{str}) =  0.69 n_{str}^{-2.5}
\end{equation}

@@

\begin{figure}
\begin{minipage}[t]{.99\linewidth}
  \centering\includegraphics[width=8.cm]{fig2} 
\end{minipage}\hfill
\caption{Volume and mass fraction of each stream, mean density of each stream in a box of size 100 $h^{-1}$ Mpc and  $128^3$ particles. Exact values of fractions, density and their curve fit for the range $n_{str} \ge 5 $ from Eq.~\ref{eq:fr_vol}, Eq.~\ref{eq:fr_mass} and Eq.~\ref{eq:den} are shown. Multi-streams are calculated with refinement factor of 8. The void ($n_{str} = 1$) occupies 93$\%$ of the volume and 55$\%$ of the mass. }
\label{fig:m_v_fr}
\end{figure}

@@

One of the advantages of using tessellation is the freedom to compute densities at very high resolutions (\cite{Abel_etal:12}, \cite{Shandarin_etal:12}). We remind that the parameter `refinement factor' denotes the ratio of separation of the particles to the separation distance of points in the diagnostic grid as defined in Sec. 3. High refinement factors are extensively used in understanding stream behaviour not only in the halo environment, but inside the halo too (Section ~\ref{sec:local}). The volume fractions of resulting number of streams are
%normalized by multi-stream field resolution (i.e. dividing by the cube of refinement factor) are %
similar for all refinement factors as
shown in bottom of the Fig. ~\ref{fig:Vfr_all} and in Table ~\ref{tab:Compare_ref}. % Hence our triangulation algorithm is universal in the sense that it is independent of the refinement factors used in tessellating the box.   
Multi-stream fields calculated on low refinement factors are more noisy at high number of streams.

With same refinement factors, the mass fractions exhibit similar pattern for same $L/N$ as well (Fig.~\ref{fig:Mfr_all}). The simulation box with highest inter-particle distance (thus least mass resolution) has more mass particles in single streaming region, as tabulated in Table~\ref{tab:Compare_LN}, but decreases steeply thereafter (Table ~\ref{tab:Compare_Slopes}). Unlike the volume fraction, the behaviour of mass fraction has a systematic variation across different refinement factors. The mass fractions given in Table ~\ref{tab:Compare_ref} show that the single-streaming regions in the multi-stream fields with refinement factors 1 and 2 have higher mass fraction than in the fields with refinement factor of 8. Decreasing the resolution from refinement factor of 8 to 1 effectively introduces smoothing of the structure. This results in growth of mass fraction in voids ($n_{str} = 1$) and decreasing it in the web ($n_{str} > 1$). The multi-stream field is more robust as one can see in Fig.~\ref{fig:Vfr_all}. and \ref{fig:Mfr_all}. In addition, the less refined multi-stream grids are prone to noise at high $n_{str}$ as usual.
\begin{figure}
\begin{minipage}[t]{.99\linewidth}
 \centering\includegraphics[width=8.cm]{fig3a} 
  \centering\includegraphics[width=8.cm]{fig3b}
\end{minipage}\hfill
\caption{Top: Volume fraction distribution of streams in 6 simulation boxes of size 100 $h^{-1}$ Mpc, 200 $h^{-1}$ Mpc 
and $128^{3}$, $256^{3}$, $512^{3}$ grids (with refinement factor of 1). Volume fractions are similar for simulation boxes with same inter-particle resolution. Slopes of the curve fits are shown in Table ~\ref{tab:Compare_Slopes}. Bottom: Volume fraction distribution for different refinement factors for 100 $h^{-1}$ Mpc, $128^{3}$ box. A considerably smoother volume fraction distribution is obtained at high number of streams in multi-stream fields with high refinement factor. }
\label{fig:Vfr_all}
\end{figure}

@@

  \centering\includegraphics[width=8.cm]{fig4a} 
  \centering\includegraphics[width=8.cm]{fig4b}
\end{minipage}\hfill
\caption{Top: Mass fraction distribution of streams in 6 simulation boxes of size 100 $h^{-1}$ Mpc, 200 $h^{-1}$ Mpc 
and $128^{3}$, $256^{3}$, $512^{3}$ grids ( with refinement factor of 1). Mass fractions are similar for simulation boxes with same inter-particle resolution. Slopes of the curve fits are shown in Table ~\ref{tab:Compare_Slopes}. Bottom: Mass fraction distribution for different refinement factors for 100 $h^{-1}$ Mpc, $128^{3}$ box. Single-streaming void regions have more fraction of mass particles in multi-stream fields calculated at low refinement factors of 1 and 2. This effect is minimized when calculation is done at better refinement. In addition, mass fraction distribution is less noisy.}
\label{fig:Mfr_all}
\end{figure}

\begin{table}
  \caption{Comparison of the approximate power law dependences of curve fits in Fig. \ref{fig:Vfr_all} and Fig. \ref{fig:Mfr_all}. Power law relations for volume fraction $f_{vol}(n_{str})$ and mass fractions $f_{mass} (n_{str}) $ as a function of number of streams at $n_{str} \geq 5$ are shown (amplitudes are not shown). The boxes of size 100 $h^{-1}$ Mpc on  $128^{3}$ grids and, 200 $h^{-1}$ Mpc on  $256^{3}$ grids have same  $L/N = 0.78 h^{-1}$ Mpc. Similarly, $L/N = 0.39 h^{-1}$ Mpc for boxes of size 100 $h^{-1}$ Mpc on  $256^{3}$ grids and, 200 $h^{-1}$ Mpc on  $512^{3}$ grids.}
\begin{tabular}{|l|r|r|r|r|}
\hline
%\multicolumn{1}{|c|}{} & \multicolumn{4}{l|}{Multi-stream analysis (This work)} & \multicolumn{4}{c|}{ORIGAMI \citep{Flack_Neyrinck:14}}    \\ \hline
$L/N$                & $0.19$ & $0.39$& $0.78$ & $1.56$  \\ \hline
$f_{vol} (n_{str}) $ Vs. $n_{str}$                 & $-2.1$   & $-2.3$    & $-2.5$      & $-2.9$  \\ \hline
$f_{mass} (n_{str}) $   Vs. $n_{str}$            & $-1.1$   & $-1.2$   & $-1.4$       & $-2.0$     \\ \hline
\end{tabular}
 \label{tab:Compare_Slopes}
\end{table}
